### 2021-07-09 msgauge-multisym.tex
Bibliography tidied up.

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Rogers embedding}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
	Consider now $\omega$ \alert{$n$-plectic}
	\vfill
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
	\end{center}
	\vfill
	\only<1-3>{
		.
	}

	\only<4->{
	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2021}.]
	\begin{itemize}[leftmargin=0pt]
		\item[$\cdot$]<4-> 
			consider the graded vector subspace $\mathcal{A}$
			\begin{displaymath}
			\mathclap{
			{\mathcal{A}^k} =
			\begin{cases}
		\left.\left\lbrace
		\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
		~ \right\vert ~
		\iota_X \omega = -d \alpha\right\rbrace
&\quad k=0,\\
				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
			\end{cases}			
			}
			\end{displaymath}						
		\item[$\cdot$]<5-> 
			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
		\item[$\cdot$]<6->

			$L_\infty(M,\omega) \cong 
				(\mathcal{A},\pi) \color{blue}\cong\color{black}
				(\mathcal{A},\mu) \hookrightarrow
				L_\infty(E^n,\omega)$
	\end{itemize}
	\end{thmblock}
	}
	\only<6->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!1,draw=orange!30,anchor=base]            
            	 (base) at ($(current page.east)-(2.25,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
            	 Complete proof\\
            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
            	 }}};
		}			
	}

\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

>>>>

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Rogers embedding}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile,t]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
	Consider now $\omega$ \alert{$n$-plectic}
	\vfill
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
	\only<4->{
	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2021}.]
	\begin{itemize}[leftmargin=0pt]
		\item[$\cdot$]<4-> 
			consider the graded vector subspace $\mathcal{A}$
			\begin{displaymath}
			\mathclap{
			{\mathcal{A}^k} =
			\begin{cases}
		\left.\left\lbrace
		\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
		~ \right\vert ~
		\iota_X \omega = -d \alpha\right\rbrace
&\quad k=0,\\
				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
			\end{cases}			
			}
			\end{displaymath}						
		\item[$\cdot$]<5-> 
			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
		\item[$\cdot$]<6->

			$L_\infty(M,\omega) \cong 
				(\mathcal{A},\pi) \color{blue}\cong\color{black}
				(\mathcal{A},\mu) \hookrightarrow
				L_\infty(E^n,\omega)$
	\end{itemize}
	\end{thmblock}
	}
	\only<6->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!1,draw=orange!30,anchor=base]            
            	 (base) at ($(current page.east)-(2.25,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
            	 Complete proof\\
            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
            	 }}};
		}			
	}
	\end{minipage}
\end{frame}
\note[itemize]{
	\item this is the "work in progress" part of the preprint.
	\begin{itemize}
		\item[-] In the 1-plectic case is extremely simple to check.
		\item[-] The 2-plectic case has been constructed by Rogers in \cite{Rogers2010}.
		\item[-] Argument about existence by Ritter and Saemann \cite{Ritter2015}.
	\end{itemize}
}
%-------------------------------------------------------------------------------------------------------------------------------------------------
